Concurrent Programming with CXL

### 2020-05-18 book/paper.tex
Better printing

\begin{figure}
\begin{code}
\begin{verbatim}
Up.cxl:1 def process(self):
   0 Jump 12
   1 Frame ('process', 'Up.cxl', 1, 5) ('self', 'Up.cxl', 1, 13) 11
Up.cxl:2     count = count + 1;
   2 Constant (1, 'Up.cxl', 2, 21)
   3 Load ('count', 'Up.cxl', 2, 13)
   4 Nary ('+', 'Up.cxl', 2, 19) 2
   5 Name ('count', 'Up.cxl', 2, 5)
   6 Store 1
Up.cxl:3     done[self] = True;
   7 Constant (True, 'Up.cxl', 3, 18)
   8 LoadVar ('self', 'Up.cxl', 3, 10)
   9 Name ('done', 'Up.cxl', 3, 5)
   10 Store 2
   11 Return
Up.cxl:5 count = 0;
   12 Constant (0, 'Up.cxl', 5, 9)
   13 Name ('count', 'Up.cxl', 5, 1)
   14 Store 1
\end{verbatim}
\end{code}
\caption{The first part of the machine code corresponding to Figure~\ref{fig:inc}.}
\label{fig:inccode}
\end{figure}

\begin{figure}
\begin{code}
\begin{verbatim}
Assertion failed ('assert', 'Up.cxl', 12, 1) 1

==== Safety violation ====
__main__ () [0,12-29]     30 { 'count': 0, 'done': { 1: False, 2: False } }
up       1  [1-5]          6 { 'count': 0, 'done': { 1: False, 2: False } }
up       2  [1-10]        11 { 'count': 1, 'done': { 1: False, 2: True  } }
up       1  [6-10]        11 { 'count': 1, 'done': { 1: True,  2: True  } }
__main__ () [30-37,39-44] 44 { 'count': 1, 'done': { 1: True,  2: True  } }
\end{verbatim}
\end{code}
\caption{The output of running Figure~\ref{fig:inc}.}
\label{fig:incoutput}
\end{figure}

>>>>

\begin{figure}
\begin{code}
\begin{verbatim}
Up.cxl:1 def process(self):
   0 Jump 12
   1 Frame ('process', 'Up.cxl', 1, 5) [('self', '<stdin>', 1, 13)] 11
Up.cxl:2     count = count + 1;
   2 Constant (1, 'Up.cxl', 2, 21)
   3 Load ('count', 'Up.cxl', 2, 13)
   4 Nary ('+', 'Up.cxl', 2, 19) 2
   5 Name ('count', 'Up.cxl', 2, 5)
   6 Store 1
Up.cxl:3     done[self] = True;
   7 Constant (True, 'Up.cxl', 3, 18)
   8 LoadVar ('self', 'Up.cxl', 3, 10)
   9 Name ('done', 'Up.cxl', 3, 5)
   10 Store 2
   11 Return
Up.cxl:5 count = 0;
   12 Constant (0, 'Up.cxl', 5, 9)
   13 Name ('count', 'Up.cxl', 5, 1)
   14 Store 1
\end{verbatim}
\end{code}
\caption{The first part of the machine code corresponding to Figure~\ref{fig:inc}.}
\label{fig:inccode}
\end{figure}

\begin{figure}
\begin{code}
\begin{verbatim}
==== Safety violation ====
__main__/() [0,12-31]           32 dict{ .count:0, .done:dict{ 0:False, 1:False } }
process/0   [1-5]                6 dict{ .count:0, .done:dict{ 0:False, 1:False } }
process/1   [1-10]              11 dict{ .count:1, .done:dict{ 0:False, 1:True  } }
process/0   [6-10]              11 dict{ .count:1, .done:dict{ 0:True,  1:True  } }
__main__/() [32-34,37-42,44-48] 49 dict{ .count:1, .done:dict{ 0:True,  1:True  } }
\end{verbatim}
\end{code}
\caption{The output of running Figure~\ref{fig:inc}.}
\label{fig:incoutput}
\end{figure}
